%% INTRODUCTION

%% HEADER

\mobile{+91 982-044-6232}
\email{chinmaydpai@gmail.com}
\homepage{maych.in}
\github{thunderbottom}
\linkedin{chinmaydpai}

%% SKILLS

\newcommand{\languages}{Python, R, Java, JavaScript, C++}
\newcommand{\devops}{Ansible, Docker, Kubernetes, *NIX Systems, AWS, LVM, LUKS,
  Vagrant, Terraform, Bash, NGiNX, Packer, MySQL, Redis, Jenkins, LXC/LXD, Prometheus,
Grafana}
\newcommand{\frameworks}{Flask, Django, Frappe Framework, Vue.js, \LaTeX}

%% EDUCATION

\newcommand{\beDegree}{
  \degree{May 2018}%
  {Bachelor of Engg.}%
  {Bachelor of Engineering}%
  {in}%
  {Computer Engineering, CGPA: 7.4/10}%
  {WIEECT, Mumbai University}%
  {}%
  {}%
{}}

%% EXPERIENCE

\newcommand{\frappe}{
  \experience{Aug 2018--- \\ Present}%
  {DevOps \& Security Engineer}%
  {at}%
  {\href{https://frappe.io}{Frappe Technologies pvt. ltd.}}%
  {\textit{A seasoned DevOps Engineer responsible for system automation,
    and design and maintenance of core and security infrastructures.}
    \begin{exlist}
    \item Incorporated ERPNext into Reliance's Tech Stack
      \begin{exlist}
      \item Led training on Frappe Framework, Python, and MariaDB at Reliance,
        for over 60 Engineers/Consultants across two weeks.
      \item Increased outbound contracts for Frappe.
      \end{exlist}
    \item Generated Comparative Analysis Reports of Hyperconverged Infrastructure (HCI)
      for LIC
      \begin{exlist}
      \item Authored a SysBench-based distributed benchmarking system for HCI under the guidance
        of \href{https://www.cse.iitb.ac.in/~damani/}{Prof. Om Damani} (IIT-B).
      \item Consolidated over 150 core-infrastructure servers across India into
        8x3-server-node HCI zones.
      \end{exlist}
    \item Led the effort to maintain and improve internal orchestration platform
      for ERPNext which included:
      \begin{exlist}
      \item Reworking the existing container platform to allow for orchestration
        and independent scaling using \href{https://github.com/frappe/frappe_docker}{Docker Swarm}
        and \href{https://helm.erpnext.com}{Kubernetes}.
      \item Improving the existing VM image generation pipeline to reduce operational
        overhead time and streamline the deployment process by reducing redundancy.
      \end{exlist}
    \item Created a new and novel SSH Certificate Authority for Frappe, ensuring
      proper authorized and secure server access.
    \item Eliminated over 30 security vulnerabilities since January 2020 and taken measures
      to improve in-house security, with issues pertaining to CSRF, RCE, SSRF, XSS, etc.
    \item Managed over 30 self-hosted ERPNext client instances.
    \item Enabled new standards for churn-analysis, site metrics, automating report
      generation and daily mailed summary with relevant account details.
    \item Engineered an in-house server running Proxmox to reduce 75\% in monthly cloud
      computing costs, while providing better service and uptime.
    \item Authored migration manager and automated cloud version upgrade, reducing manual
      intervention for system upgrades by 95\%.
    \item Completely rewrote the File API and refactored the Email module inside
      the Frappe Framework.
    \item Authored deployer-bot, a bot for deploying test instances on DigitalOcean through
      GitHub pull requests.
  \end{exlist}}
}

%% PROJECTS

\newcommand{\pyroxmox}{
  \proj{Pyroxmox}%
  {A novel dynamic \python API for Proxmox VE. Primarily
    intended to be used to effortlessly spawn instances on the
  in-house server.}%
  {git.maych.in/thunderbottom/pyroxmox}
}

\newcommand{\ultimatebrowser}{
  \proj{Ultimate Browser Project}%
  {An Open-Source \android browser based on WebView which had
    over 100,000 downloads through XDA Forums and around 60,000
  concurrent sessions in April 2015.}%
  {github.com/thunderbottom/ultimatebrowserproject}
}

%% EXTRACURRICULAR

\newcommand{\activities}{
  \begin{exlist}
  \item Presented a talk on ``SSH Security Standards and Practices at Frappe'' at the ERPNext Conference 2019.
  \item Actively maintaing a fork of the Linux Kernel.
  \item Programmatically \href{https://soundcloud.com/harmonicseventhnoiseprotocol}{composing music} using FoxDot.
  \end{exlist}
}

